Cluster Difference Imaging Photometric Survey (CDIPS) II: Validatation of a Jupiter-Sized Planet in IC~2602

### 2020-06-17 paper/ms.tex
minor words

>>>>

IC~2602 happens to be near the western edge of the Sco OB2
association, and is relatively close to it in proper motion space
(Damiani+2019).
Damini+2019 also reported evidence for the ongoing evaporation of
\cn, in the form of a diffuse halo of young stars around the central
density cusps.

While \cn\ is older than most known Sco OB2 members,
